Natural Stories LM analysis

### 2020-07-21 Analysis/nat_stories_gam.Rmd
add density to the gam plot

---
title: "Natural Stories GAM analysis"
output: github_document
---
```{r, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F)
options(knitr.table.format = "html")
library(tidyverse)
library(readr)
library(brms)
library(lme4)
library(rstan)
library(tidybayes)
library(knitr)
library(mgcv)
library(mgcViz)
library(tidymv)
library(rsample)
theme_set(theme_bw())
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

@@

ngram_data <- labelled_pre_error %>% select(rt, surprisal=ngram_surp, prev_surp=past_ngram, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            )

grnn_data <- labelled_pre_error %>% select(rt, surprisal=grnn_surp, prev_surp=past_grnn, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            )

txl_data <- labelled_pre_error %>% select(rt, surprisal=txl_surp, prev_surp=past_txl, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            )

@@

a <- get_gam_predictions(model=gam_ngram_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Current")
b <- get_gam_predictions(model=gam_ngram_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Previous")
c <- get_gam_predictions(model=gam_grnn_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Current")
d <- get_gam_predictions(model=gam_grnn_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Previous")
e <- get_gam_predictions(model=gam_txl_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Current")
f <- get_gam_predictions(model=gam_txl_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Previous")

all <- a %>% union(b) %>% union(c) %>% union(d) %>% union(e) %>% union(f)

ggplot(all, aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
  facet_grid(s~model)+
  labs(x="Surprisal (bits)", y="Reaction Time (ms)")

ggsave("../Papers/gam.pdf", width=3.5, height=2, unit="in")

>>>>

---
title: "Natural Stories GAM analysis"
output: github_document
---
```{r, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F)
options(knitr.table.format = "html")
library(tidyverse)
library(readr)
library(brms)
library(lme4)
library(rstan)
library(tidybayes)
library(knitr)
library(mgcv)
library(mgcViz)
library(tidymv)
library(rsample)
library(cowplot)
library(scales)
theme_set(theme_bw())
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

@@

ngram_data <- labelled_pre_error %>% select(rt, surprisal=ngram_surp, prev_surp=past_ngram, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            ) %>% mutate(model="5-gram")

grnn_data <- labelled_pre_error %>% select(rt, surprisal=grnn_surp, prev_surp=past_grnn, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            )%>% mutate(model="GRNN")

txl_data <- labelled_pre_error %>% select(rt, surprisal=txl_surp, prev_surp=past_txl, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            ) %>% mutate(model="TXL")

all_data <- ngram_data %>% union(grnn_data) %>% union(txl_data) %>% 
  select(surprisal, prev_surp,model) %>% 
  pivot_longer(cols=`surprisal`:`prev_surp`) %>% 
  mutate(s=ifelse(name=="surprisal", "Current","Previous"))
```

@@

a <- get_gam_predictions(model=gam_ngram_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Current")
b <- get_gam_predictions(model=gam_ngram_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Previous")
c <- get_gam_predictions(model=gam_grnn_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Current")
d <- get_gam_predictions(model=gam_grnn_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Previous")
e <- get_gam_predictions(model=gam_txl_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Current")
f <- get_gam_predictions(model=gam_txl_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Previous")
```

```{r}
all <- a %>% union(b) %>% union(c) %>% union(d) %>% union(e) %>% union(f)

gam1 <-  ggplot(all, aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
   #geom_density(data=all_data, aes(x=value), fill="gray",)+
  facet_grid(s~model)+
  coord_cartesian(ylim=c(700,1300), xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

dens2 <-   ggplot(all_data, aes(x=value))+
  geom_density(fill="gray",)+
  facet_grid(.~model)+
  labs(x="Surprisal (bits)", y="")+
  theme(axis.text.y = element_blank(), strip.text=element_blank(), axis.ticks.y =element_blank(), axis.title.y=element_blank(), panel.grid=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "cm"))

bot <- plot_grid(NA, dens2, NA, nrow=1, rel_widths = c(.16, 1, .08))

 plot_grid(gam1, bot, nrow=2, rel_heights = c(1, .3))

ggsave("../Papers/gam.pdf", width=4, height=2.3, unit="in")

### 2020-07-21 Analysis/nat_stories_lms.Rmd
add density to the gam plot

```{r}
# a <- log_lik(brm_ngram_interact)
# 
# a2 <- add_criterion(brm_ngram_interact, "waic")
# 
# b <- log_lik(brm_grnn_interact)
# 
# c <- log_lik(brm_txl_interact)
```

>>>>

```{r}
 a <- log_lik(brm_ngram_interact)

a2 <- exp(a*-1) %>% mean()
# a2 <- add_criterion(brm_ngram_interact, "waic")
# 
 b <- log_lik(brm_grnn_interact)

 b2 <- exp(a*-1) %>% mean()
 c <- log_lik(brm_txl_interact)
 c2 <- exp(c*-1) %>% mean()

 product <- sum(a)

 a2 <- a*-1+product
```
